Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
More TODOs
Rearranged graphs

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{image_window}
    \caption{\label{image_window} Accuracy of $ImageConv(\iota)$ compared to Acoustic Parameter at discriminating between run types (85\% accuracy).}
\end{figure}

@@

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{grav_opt_validation}
    \caption{\label{grav_opt_validation} Accuracy of optimal gravitational differentiation training run compared to Acoustic Parameter (98\% accuracy).}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{grav_acc_by_hyper}
    \caption{\label{grav_acc_by_hyper} Accuracy of gravitational differentiation as a function of hyperparameter values.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{icn_acc_by_hyper}
    \caption{\label{icn_acc_by_hyper} Mean accuracy of iterative cluster nucleation as a function of hyperparameter values.}
\end{figure}

@@

\begin{tabular}{|l|l|l|}
    \hline
    Technique & Max AP Accuracy & Max Mean by Run \\
    \hline
    Gravitational Differentiation (256 $\varsigma$) & 98\% & 96\% \\
    \hline
    Gravitational Differentiation (128 $\varsigma$) & TODO & TODO \\
    \hline
    Iterative Cluster Nucleation (256 $\varsigma$) & 100\% & 98\% \\
    \hline
    Iterative Cluster Nucleation (128 $\varsigma$) & TODO & TODO \\
    \hline
    Existing NN TODO & X & X \\
    \hline
    AP TODO & X & X \\
    \hline
\end{tabular}

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}

@@

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{image_window}
    \caption{\label{image_window} Accuracy of $ImageConv(\iota)$ compared to Acoustic Parameter at discriminating between run types (85\% accuracy).}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{grav_opt_validation}
    \caption{\label{grav_opt_validation} Accuracy of best gravitational differentiation training run compared to Acoustic Parameter (98\% accuracy).}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{grav_acc_by_hyper}
    \caption{\label{grav_acc_by_hyper} Accuracy of gravitational differentiation as a function of hyperparameter values.}
\end{figure}

@@

@@

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{icn_acc_by_hyper}
    \caption{\label{icn_acc_by_hyper} Mean accuracy of iterative cluster nucleation as a function of hyperparameter values.}
\end{figure}

@@

\begin{tabular}{|l|l|l|l|}
    \hline
    Technique & Max AP Accuracy & Max Mean by Run & Class-Wise SD \\
    \hline
    Gravitational Differentiation (256 $\varsigma$) & 98\% & 96\% & TODO \\
    \hline
    Gravitational Differentiation (128 $\varsigma$) & TODO & TODO & TODO \\
    \hline
    Iterative Cluster Nucleation (256 $\varsigma$) & 100\% & 98\% & TODO \\
    \hline
    Iterative Cluster Nucleation (128 $\varsigma$) & TODO & TODO & TODO \\
    \hline
    Existing NN TODO & X & X & X \\
    \hline
    AP TODO & X & X & X \\
    \hline
\end{tabular}
